---
title: "ShinyDemo"
author: Jason Bryer, Ph.D.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ShinyDemo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ShinyDemo)
```

[Shiny](https://shiny.rstudio.com) applications have become a very popular and powerful way of creating interactive we applications that leverage the power of R. There are numerious ways Shiny apps can be deployed including [ShinyApps.io](https://www.shinyapps.io) or hosted services such as DigitalOcean or Amazon AWS. The [Golem](https://github.com/ThinkR-open/golem) project provides a framework for developing Shiny apps as R packages. However, with Golem, the Shiny app is the primary product. This package provides a framework for including Shiny apps where the app is designed to demonstrate the features of the package. That is, it is more like the role R package demos had before they were obfuscated by package vignettes and tests (via the [`usethis`](https://usethis.r-lib.org) package. The primary function used by package users is `shiny_demo`. Much like the build in `demo()` function, calling `shiny_demo()` without any parameters will list available Shiny demo apps in all the loaded packages. Calling `shiny_demo(topic)` will launch the Shiny app. In addition to providing a standardized structure for including Shiny demo apps within your package, it also provides functionality to allow the package user to pass parameters to the Shiny app.

For the package developer, Shiny demo apps need to be placed in the `inst/shiny` folder. The `ShinyDemo::shiny_demo()` function will automatically find apps located there. 



```{r, eval=FALSE}
fluidPage(
	titlePanel("Data Frame Viewer"),
	uiOutput('df_select'),
	tabsetPanel(
		tabPanel(
			'Structure',
			verbatimTextOutput('df_structure')
		),
		tabPanel(
			'Table',
			dataTableOutput('df_table')
		)
	)
)
```


```{r, eval=FALSE}
function(input, output, session) {
	get_data <- reactive({
		req(input$dataframe)
		df <- NULL
		if(exists(input$dataframe)) {
			df <- get(input$dataframe)
		}
		return(df)
	})
	
	output$df_select <- renderUI({
		ls_out <- ls_all()
		dfs <- character()
		for(i in ls_out) {
			if(is.data.frame(get(i))) {
				dfs <- c(dfs, i)
			}
		}
		if(length(dfs) > 0) {
			selectInput('dataframe', 'Select Data Frame', choices = dfs)
		} else {
			p('No data.frames found!')
		}
	})
	
	output$df_structure <- renderPrint({
		df <- get_data()
		str(df)
	})
	
	output$df_table <- renderDataTable({
		df <- get_data()
		return(df)
	})
}
```


```{r, eval=FALSE}
shiny_demo('df_viewer')
shiny_demo('df_viewer',
		   motor_trend_cars = mtcars,
		   old_faithful = faithful)
```
